draft-data

### 2024-11-25 draftdata.Rmd
whynooooworkstill

<title>My Descriptives</title>

@@

```{=html}
<style>
body {
text-align: left;
line-height: 1.5;
}

h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
  line-height: 1;
}

</style>
```

@@

The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them and are often called co-authorships. The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2, @rvest). The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period.

**I**n the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another. This means each actor has both outdegrees and indegrees. Outdegrees refer to 'sent' connections that refer to being the first author of a publication. Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author. The generated adjacency matrix is thus holds a network, indicating the collaboration patterns of the academics at Radboud University between 2015-2018.

@@

The scholars' h-indices will serve as a control variable in this research design (@Bornmann2020, @Bornmann2021). The h-index calculates the number of publications that have been cited at least as frequently as the author's total number of publications. This number can then be used as measure for the author's 'prestige' (@Hirsch2005). The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by Lucan Bovens.

@@

```{r sum gender, echo=FALSE }
summary(df_ego$gender)
```

@@

```{r counts gender-all, echo=FALSE }
table(df_ego$gender)
```

@@

```{r histogram gender, echo=FALSE }
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

```{r gender per dep., echo=FALSE }

@@

```{r summary h index, echo=FALSE }
summary(df_ego$h_index)
```

@@

```{r hist h index, echo=FALSE }
# Histogram of prestige scores for Wave 1

@@

```{r table per dep h index, echo=FALSE }
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

>>>>

<title>My Data</title>

@@

@@

The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them and are often called co-authorships. The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2, @rvest). The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave. Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period.

In the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another. This means each actor has both outdegrees and indegrees. Outdegrees refer to 'sent' connections that refer to being the first author of a publication. Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author. The generated adjacency matrix is thus holds a network, indicating the collaboration patterns of the academics at Radboud University between 2015-2018.

@@

The scholars' h-indices will serve as a control variable in this research design (@Bornmann2020, @Bornmann2021). The h-index calculates the number of publications that have been cited at least as frequently as the author's total number of publications. This number can then be used as measure for the author's 'prestige' (@Hirsch2005). The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022). The code for this process was provided by Lucan Bovens.

@@

```{r sum gender, echo=FALSE}
summary(df_ego$gender)
```

@@

```{r counts gender-all, echo=FALSE}
table(df_ego$gender)
```

@@

```{r histogram gender, echo=FALSE}
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

```{r gender per dep., echo=FALSE}

@@

```{r summary h index, echo=FALSE}
summary(df_ego$h_index)
```

@@

```{r hist h index, echo=FALSE}
# Histogram of prestige scores for Wave 1

@@

```{r table dep h index, echo=FALSE}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```
